A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-01-13 paper.Rmd
Added some small changes to affliation and funding

3 = University of California, Berkeley, USA

@@

- Mile McBain
- Anna Krystalli
- Daniella Lowenberg
- ACEMS International Mobility Programme

>>>>

3 = Berkeley Institute for Data Science, University of California, Berkeley, USA

@@

- Mile McBain
- Anna Krystalli
- Daniella Lowenberg
- ACEMS International Mobility Programme
- Helmsley Charitable Trust, Gordon and Betty Moore Foundation, Sloan Foundation.
